% Jason Ajmo, Patrick Grasso, Nicholas Massa, Bradford Smith and Nicholas Zubrycki
% CS 546 Final Project proposal.tex
% 03/20/2016
% "We pledge our honor that we have abided by the Stevens Honor System."
% ======================================================================

% global document styles =======================================================
\documentclass[11pt, letterpaper]{article}
\usepackage[letterpaper, margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tgbonum}
\usepackage{textcomp}
\usepackage{xcolor} %for colored code formatting
\pagestyle{empty}
\setlength{\tabcolsep}{0em}


% custom macros ================================================================
% simple inline code formatting (using typewriter font)
%\newcommand{\code}[1]{\texttt{#1}}

% colored inline code formatting
\definecolor{codebg}{RGB}{225,225,225}
\definecolor{codefg}{RGB}{200,40,90}
\newcommand{\code}[1]{\colorbox{codebg}{\textcolor{codefg}{\texttt{#1}}}}


% document begins here =========================================================
\begin{document}
\noindent{Jason Ajmo, Patrick Grasso, Nicholas Massa, Bradford Smith and Nicholas Zubrycki}\\
\noindent{CS 546 Final Project Proposal}\\
\noindent{\today}\\
\noindent{\textit{``We pledge our honor that we have abided by the Stevens Honor System.''}}\\

\noindent{\Large{Group}}

\begin{itemize}
    \item[\textbullet]Jason Ajmo
    \item[\textbullet]Patrick Grasso
    \item[\textbullet]Nicholas Massa
    \item[\textbullet]Bradford Smith
    \item[\textbullet]Nicholas Zubrycki
\end{itemize}


\noindent{\Large{Description}}

\bigskip

Our project will be a movie management system. Upon logging in, a user will be able to manage their movies to watch and movies they've seen. Upon adding a movie, relevant metadata will automatically be fetched from online sources. A user would be able to give a movie a rating, and mark it as ``seen'', ``going to watch'', or ``not going to watch''. A user can search their saved movies by genre, title, year, or a combination of all three.

\bigskip

\noindent{\Large{Core Features}}

\begin{itemize}
    \item[\textbullet]Marking movies as ``seen'', ``going to watch'', or ``not going to watch''. The default option will be configurable.
    \item[\textbullet]Being able to search movies based on multiple criteria.
    \item[\textbullet]Adding new movies to the user's profile.
    \item[\textbullet]Fetching metadata automatically. The default source will the be configurable.
\end{itemize}

\noindent{\Large{Extras}}

\begin{itemize}
    \item[\textbullet]Redis.
    \item[\textbullet]Machine learning to suggest new movies to watch.
\end{itemize}
\end{document}

